\documentclass[12pt,letterpaper]{article}
\usepackage{anysize}
\marginsize{2cm}{2cm}{1cm}{1cm}

\begin{document}

\begin{titlepage}
    \vspace*{4cm}
    \begin{flushright}
    {\huge
        ECE 375 Lab 1\\[1cm]
    }
    {\large
        Introduction to AVR Tools
    }
    \end{flushright}
    \begin{flushleft}
    Lab Time: Monday Noon-2:00pm
    \end{flushleft}
    \begin{flushright}
    Ian Kronquist
    \vfill
    \rule{5in}{.5mm}\\
    TA Signature
    \end{flushright}

\end{titlepage}

\section{Prelab}
    turn right
The answers to the prelab questions can be found in the AVR Starters Guide and
the AVR Instruction Set.
\begin{enumerate}
    \item What is the stack pointer? How is the stack pointer used and how do
    you initialize it? Provide pseudo-code (NOT actual assembly code) that
    illustrates how to initialize the stack pointer.\\
    The stack pointer is a special register which always contains the address
    of the top of the stack. It is somewhat analogous to the program
    counter.
    \item What does the AVR instruction LPM do and how do you use it? Provide
    pseudo-code that shows how to use the LPM instruction.\\
    The $LPM$ instruction takes whatever address is in the $Z$ register, and
    loads it into the provided register. Since program memory is organized into
    16-bit words, and $LPM$ only loads one byte, the least significant bit of
    the $Z$ register indicates whether to load the low byte of the 16 bit
    memory location or the high bit. Optionally, the address in the $Z$
    register can be incremented.
    \begin{verbatim}
    lpm r1, Z ; Loads the value pointed to by the address 
              ; in the Z register into the r1 register.
    \end{verbatim}
    \item Look at the definition file $m128def.inc$. What is contained within
    this definition file? What are the benefits of using this definition file?
    How would you include it into your AVR Assembly program?\\
    The $m128def.inc$ file contains a series of $.equ$ directives which
    initialize constants used for accessing ports and pins on the board.
    To include this file you would use the $.include$ directive.
    \begin{verbatim}
    .include "./m128def.inc"
    \end{verbatim}
\end{enumerate}

\end{document}
